Contextual Combinatorial Cascading Bandits

### 2015-12-05 contextual combinatorial cascading bandits.tex
log ->ln, \Delta->R

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
$$
\beta_{t}(\delta) = \sqrt{\log(\det(\bV_{t})) + 2 \log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \beta_{t}(\delta).
\end{equation}
\end{theorem}

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\log(\det(\bV_{t})) + 2 \log(\frac{1}{\delta})} + \sqrt{\lambda}$}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time 
	that an action could have all base arms observed under the 
disjunctive objective. The following is the main theorem on the regret achieved by
	our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$,
	where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. 
Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\log(\lambda + C_\gamma T/d)}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \log T\right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\log(\lambda + C_\gamma T/d)} \nonumber \\
&\qquad \cdot \left(\sqrt{d\log(\lambda + C_\gamma T/d) + 2\log\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \log T\right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

\wei{Is the $\log$ in the above theorem with base $2$? 
	Other UCB regret bounds usually has $\ln$. Please double check if here
	indeed we use $\log$ of base 2. }
To prove Theorem \ref{thm:main}, we could start from estimating $\EE[\Delta_{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\wei{I did not see $\Delta_{t,\bA_t}$ defined before.}
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
\Delta_{t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
\Delta_{\wedge, t,A} \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

So if the chosen action $\bA_t$ is not suboptimal, which means
$$
f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
$$
Then we can derive an estimate of $\Delta_{t, \bA_t}$ and $\Delta_{\wedge, t, \bA_t}$, however, in terms of all base arms in $\bA_t$. Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
\begin{align*}
&~~\EE_t[\Delta_{t, \bA_t}] \\
&= \EE_t[\Delta_{t, \bA_t}(1/p_{t, \bA_t}) \bOne\{\Delta_{t, \bA_t} > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[\Delta_{\wedge, t, \bA_t}] \\
&= \EE_t[\Delta_{\wedge, t, \bA_t}(1/p_{\wedge, t, \bA_t}) \bOne\{\Delta_{\wedge, t, \bA_t} > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

@@

\begin{lemma}
\label{lem:prefixExist}
Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
$$
p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad \Delta_{\wedge, t, \bB_t} \geq \frac{1}{2} \Delta_{\wedge, t, \bA_t}.
$$
\end{lemma}
From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $\Delta_{\wedge, t, \bB_t}$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[\Delta_{\wedge, t, \bA_t}|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[\Delta_{\wedge, t, \bA_t}|\cH_{t-1}]$, thus for $R_{\wedge}(T)$. We leave all details in the next subsection.

@@

\begin{proof}[ of Lemma \ref{lem:DeltaEstimate}]
By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ \eqref{eq:defU},
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
\Delta_{t, A} = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the disjunctive case can be deduced similarly.
\end{proof}

@@

\begin{lemma}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad \Delta_{\wedge, t, B} \geq \frac{1}{2}\Delta_{\wedge, t, A}.
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
$$
p_{\wedge, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

@@

\begin{proposition}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[\Delta_{t, \bA_t}|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[\Delta_{\wedge, t, \bA_t}|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{proposition}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $\Delta_{\wedge, \bB_t} \geq \frac{1}{2}\Delta_{\wedge, A}$. Then we have
$$
\EE_t[\Delta_{\wedge, t, \bA_t}] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[\Delta_{\wedge, t, \bB_t} \bOne\{\Delta_{\wedge, t, \bB_t} > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
\Delta_{\wedge, t, \bB_t} \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\log(\det(\bV_t)).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\log(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\log(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\log(\det(\bV_t)) - \log(\det(\lambda I))) < 2\log(\det(\bV_t))
\end{align*}
\end{proof}

>>>>

\begin{theorem}[\cite{abbasi2011improved}]
\label{thm:theta_estimate}
Let 
$$
\beta_{t}(\delta) = \sqrt{\ln(\frac{\det(\bV_{t})}{\det(\lambda I)}) + 2 \ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}.
$$
Then for any $\delta > 0$, with probability at least $1 - \delta$, for all $t > 0$, we have
\begin{equation}
\label{eq:estimateTheta}
\norm{\hat{\theta}_t - \theta_{\ast}}_{\bV_{t}} \leq \beta_{t}(\delta).
\end{equation}
\end{theorem}

@@

\STATE {//Update statistics}
\STATE {$\bV_{t} \leftarrow \bV_{t-1} + \sum_{k=1}^{\bO_t} \gamma_k^2 x_{t, \ba_k^t}x_{t, \ba_k^t}^{\top}$}
\STATE {$\bX_t \leftarrow [\bX_{t-1}; ~\gamma_1 x_{t, \ba_1^t}^{\top};  ~\ldots; ~\gamma_{\bO_t} x_{t, \ba_{\bO_t}^t}^{\top}]$}
\STATE {$\bY_t \leftarrow [\bY_{t-1}; ~\gamma_1 \bw(\ba_1^t); ~\ldots; ~\gamma_{\bO_t} \bw_t(\ba_{\bO_t}^t)]$}
\STATE {$\hat{\theta}_t \leftarrow (\bX_t^\top \bX_t + \lambda I)^{-1} \bX_{t}^\top \bY_t$}
\STATE {$\beta_{t}(\delta) \leftarrow \sqrt{\ln(\det(\bV_{t})) + 2 \ln(\frac{1}{\delta})} + \sqrt{\lambda}$}

@@

To state our main theorem, we need some definitions. Let
$$
f_{\wedge}^* = \max_{1 \leq t \leq T} f_{\wedge, t}^{\ast}
$$
denote the best expected reward of all time under the conjunctive objective.
Let $p_{t, A}$ (resp., $p_{\wedge, t, A}$) be the probability that all base arms of $A = (a_1, \ldots, a_{\abs{A}})$ have been observed under the disjunctive objective (resp., conjunctive objective) when under the context of time $t$, that is 
\begin{align*}
&p_{t, A} = \prod_{k=1}^{\abs{A}-1} (1 - \theta_{\ast}^{\top} x_{t, a_k^t}),\\
&p_{\wedge, t, A} = \prod_{k=1}^{\abs{A}-1} (\theta_{\ast}^{\top} x_{t, a_k^t}).
\end{align*}
We also define $p^* = \min_{1 \leq t \leq T} \min_{A \in \cS} ~ p_{t, A}$ to be the minimal probability over all time that an action could have all base arms observed under the disjunctive objective. The following is the main theorem on the regret achieved by our C$^3$-UCB algorithm, for both the disjunctive and conjunctive objectives.
\begin{theorem}
\label{thm:main}
Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 0$ and 
$\gamma_k' = 1 - \gamma_k, \gamma'_K \leq \frac{1}{4}f_{\wedge}^{\ast}$.
Let regularization parameter $\lambda$ satisfy $\lambda \geq C_\gamma$, where $C_\gamma = \sum_{k=1}^{K} \gamma_k^2$. Then for any $\delta > 0$, with probability at least $1 - \delta$, the cumulative expected regrets of our algorithm, C$^3$-UCB for both the conjunctive and disjunctive objectives, satisfy
\begin{align}
R(T) &\le \frac{\sqrt{2}}{p^*} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))}  \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{p^*} \sqrt{TK} \ln T\right),
\end{align}
\begin{align}
R_{\wedge}(T) &\le \frac{\sqrt{128}}{f_{\wedge}^{\ast}} \sqrt{TKd\ln(1 + C_\gamma T/(\lambda d))} \nonumber \\
&\qquad \cdot \left(\sqrt{d\ln(1 + C_\gamma T/(\lambda d)) + 2\ln\left(\frac{1}{\delta}\right)} + \sqrt{\lambda}\right) \nonumber \\
&=O\left(\frac{d}{f_{\wedge}^{\ast}}\sqrt{TK} \ln T\right).
\end{align}
%where
%\begin{align*}
%C_\gamma = \sum_{k=1}^{K} \gamma_k^2 = \sum_{k=1}^{K} (1 - \gamma_k')^2 \in [1, K].
%\end{align*}
\end{theorem}

\wei{Is the $\log$ in the above theorem with base $2$? 
	Other UCB regret bounds usually has $\ln$. Please double check if here
	indeed we use $\log$ of base 2. }
\shuai{The all $\log$'s have base e. I have changed them to be $\ln$.}
To prove Theorem \ref{thm:main}, we could start from estimating $\EE[R{t, \bA_t}|\cH_t]$ for every time $t$. In fact, we can derive the following lemma.
\wei{I did not see $\Delta_{t,\bA_t}$ defined before.}
\shuai{Sorry. It should be $R(t, \bA_t)$ here. I have revised them all.}
\begin{lemma}
\label{lem:DeltaEstimate}
For any time $t$ and $A = (a_1, \ldots, a_{\abs{A}})$, if $f(A_t^*, \bU_t) \leq f(A, \bU_t)$, then we have
$$
R(t,A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}};
$$
if $f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(A, \bU_t)$, then we have
$$
R_{\wedge}(t, A) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t,a_k}}_{\bV_{t-1}^{-1}}.
$$
\end{lemma}

So if the chosen action $\bA_t$ is not suboptimal, which means
$$
f(A_t^*, \bU_t) \leq f(\bA_t, \bU_t), ~~ f_{\wedge}(A_t^*, \bU_t) \leq f_{\wedge}(\bA_t, \bU_t).
$$
Then we can derive an estimate of $R(t, \bA_t)$ and $R_{\wedge}(t, \bA_t)$, however, in terms of all base arms in $\bA_t$. Only when the learning agent has observed all base arms of $\bA_t$, we can use such an estimate, which means we are able to estimate
\begin{align*}
&~~\EE_t[R(t, \bA_t)] \\
&= \EE_t[R(t, \bA_t)(1/p_{t, \bA_t}) \bOne\{R(t, \bA_t) > 0, \bO_t \geq \abs{\bA_t}\}],\\
&~~\EE_t[R_{\wedge}(t, \bA_t)] \\
&= \EE_t[R_{\wedge}(t, \bA_t)(1/p_{\wedge, t, \bA_t}) \bOne\{R_{\wedge}(t, \bA_t) > 0, \bO_{\wedge, t} \geq \abs{\bA_t}\}].
\end{align*}

@@

\begin{lemma}
\label{lem:prefixExist}
Let $B_k = (\ba_1^t, \ldots, \ba_k^t), k \leq \abs{A}$ be a prefix of $\bA_t$. Then there exists a prefix $\bB_t$ of $\bA_t$ such that
$$
p_{\wedge, t, \bB_t} \geq \frac{1}{2} f_{\wedge, t}^* - \gamma_{\abs{\bB_t}}, \qquad R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t).
$$
\end{lemma}
From this lemma, we can use the prefix $\bB_t$ to substitue $\bA_t$ because $p_{\wedge, t, \bB_t}$ is large enough and $R_{\wedge}(t, \bB_t)$ will not be too small. Then follow the above deductions, we can get a good estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$ in terms of $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$. Once we have estimated $\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}$ and $\beta_{t-1}(\delta)$, we can get an estimate for $\EE[R_{\wedge}(t, \bA_t)|\cH_{t-1}]$, thus for $R_{\wedge}(T)$. We leave all details in the next subsection.

@@

\begin{proof}[ of Lemma \ref{lem:DeltaEstimate}]
By Lemma \ref{lem:estimateU}, $\theta_{\ast}^{\top}x_t \leq \bU_t$. Then by Lemma \ref{lem:increasing},
$$
f_t^{\ast} = f(A_t^{\ast}, \theta_{\ast}^{\top}x_t) \leq f(A_t^{\ast}, \bU_t).
$$
By Lemma \ref{lem:estimateTech} and the definition of $\bU_t$ \eqref{eq:defU},
$$
f(A, \bU_t) \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Because $f(A_t^{\ast}, \bU_t) \leq f(A, \bU_t)$, then 
$$
f_t^{\ast} \leq f(A, \theta_{\ast}^{\top}x_t) + \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
Therefore,
$$
R(t, A) = f_t^{\ast} - f(A, \theta_{\ast}^{\top}x_t) \leq \sum_{k=1}^{\abs{A}} \gamma_k \beta_{t-1}(\delta)\norm{x_{t, a_k^t}}_{\bV_{t-1}^{-1}}.
$$
The result for the disjunctive case can be deduced similarly.
\end{proof}

@@

\begin{lemma}
Suppose $0 \leq \gamma_1' \leq \cdots \leq \gamma_K' \leq 1$. Let $A = (a_1, ..., a_{\abs{A}})$. For the time $t$ and the conjunctive objective, there exists a prefix $B$ of $A$ such that 
$$
p_{\wedge, B} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{B}}', \qquad R_{\wedge}(t, B) \geq \frac{1}{2} R_{\wedge}(t, A).
$$ 
\end{lemma}
\begin{proof}
If $f_{\wedge}(A, w) \geq \frac{1}{2} f_{\wedge, t}^{\ast}$, then by Lemma \ref{lem:prefixRelation},
$$
p_{\wedge, A} \geq \frac{1}{2}f_{\wedge, t}^{\ast} - \gamma_{\abs{A}}'.
$$

@@

\begin{proposition}
Let $1 \geq \gamma_1 \geq \cdots \geq \gamma_K \geq 0$ and $\gamma_k' = 1 - \gamma_k$. Suppose the equation (\ref{eq:estimateTheta}) holds for all time $t$. Then
$$
E[R(t, \bA_t)|\cH_t] \leq \frac{1}{p^*} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}
$$
If we have
% $$
% \gamma_K \geq (1+\frac{1}{n_0})f^{\ast}, \qquad 
% $$
$$
\gamma_K' \le \frac{1}{4} f_{\wedge}^{\ast},
$$
then
\begin{align*}
% &E[\Delta_{t, \bA_t}|\cH_t] \leq (n_0+1) \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},\\
&E[R_{\wedge}(t, \bA_t)|\cH_t] \leq \frac{8}{f_{\wedge}^{\ast}} \beta_{t-1}(\delta)\sum_{k=1}^{\bO_t}\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}},
\end{align*}
where $f^{\ast} = \max_{t} f_t^{\ast}, f_{\wedge}^{\ast} = \max_{t} f_{\wedge, t}^{\ast}$.
\end{proposition}
\begin{proof}
For the disjunctive case,  $p_{\bA_t} \geq p^*$ by definition and the result can be derived directly.
% $p_{\bA_t} \geq \frac{1}{n_0 + 1}$ by lemma \ref{lem:prefixRelation} and the result can be derived directly.

For the conjunctive case, there exists a prefix $\bB_t$ of $\bA_t$ such that $p_{\wedge, \bB_t} \geq \frac{1}{4}f_{\wedge, t}^*$ and $R_{\wedge}(t, \bB_t) \geq \frac{1}{2} R_{\wedge}(t, \bA_t)$. Then we have
$$
\EE_t[R_{\wedge}(t, \bA_t)] \leq \frac{8}{f_{\wedge, t}^*} \EE_t[R_{\wedge}(t, \bB_t) \bOne\{R_{\wedge}(t, \bB_t) > 0, \bO_t \geq \abs{\bB_t}\}
$$
Because 
$$
f_{\wedge}(A_t^*, \theta_*^{\top}X_t) \leq f_{\wedge}(A_t^*,\bU_t) \leq f_{\wedge}(\bA_t,\bU_t) \leq f_{\wedge}(\bB_t,\bU_t)
$$
by Lemma \ref{lem:increasing} and
$$
f_{\wedge}(\bB_t,\bU_t) \leq f_{\wedge}(\bB_t, \theta_*^{\top}x_t) + \sum_{k=1}^{\abs{\bB_t}}\gamma_k\beta_{t-1}(\delta)\norm{x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
by Lemma \ref{lem:estimateTech}, we have
$$
R_{\wedge}(t, \bB_t) \leq \sum_{k=1}^{\abs{\bB_t}}\beta_{t-1}(\delta)\norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}.
$$
\end{proof}

@@

\begin{lemma}
If $\lambda \geq C_\gamma$, then
$$
\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2\ln(\frac{\det(\bV_t)}{\det(\lambda I)}).
$$
\end{lemma}
\begin{proof}
\begin{align*}
&\det(\bV_t) = \det(\bV_{t-1} + \sum_{k=1}^{\bO_t} (\gamma_k X_{t,\ba_k^{t}})(\gamma_k X_{t, \ba_k^{t}}^{\top}))\\
&=\det(\bV_{t-1})\\
&~~~\cdot \det(I + \sum_{k=1}^{\bO_t} \gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}} (\gamma_k \bV_{t-1}^{-1/2}x_{t,\ba_{k}^{t}})^{\top})\\
&\geq \det(\bV_{t-1}) (1 + \sum_{k=1}^{\bO_t} \norm{\gamma_k x_{t,\ba_k^t}}_{\bV_{t-1}^{-1}}^2)\\
&\geq \det(\lambda I)\prod_{s=1}^{t}(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)
\end{align*}
Because
$$
\norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \norm{\gamma_k x_{s,\ba_k^s}}_2^2/\lambda_{\min}(\bV_{s-1}) \leq \gamma_k^2 /\lambda,
$$
we have 
$$
\sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2 \leq \frac{1}{\lambda} \sum_{k=1}^{K} \gamma_k^2 = C_\gamma /\lambda \leq 1
$$
Using the fact that $ 2\ln(1+u) \geq u$ for any $u \in [0,1]$, we get
\begin{align*}
&\sum_{s=1}^t \sum_{k=1}^{\bO_s}\norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \\
&\leq 2\sum_{s=1}^t\ln(1 + \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_k^s}}_{\bV_{s-1}^{-1}}^2)\\
&\leq 2(\ln(\det(\bV_t)) - \ln(\det(\lambda I))) \\
&= 2 \ln(\frac{\det(\bV_t)}{\det(\lambda I)})
\end{align*}
\end{proof}
